How One Microtask Affects Another

### 2015-09-24 docs/publications/2015.08_CHI/man.tex
edwards final pass

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotation.
Here we identify a feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
discover that earlier tasks have a priming effect on the worker, shifting 
the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to the overt framing of the assignment, 
effected by stating the requester's research interest, 
and find that intertask effects are on par or stronger.
While intertask effects can be a source of systematic bias, 
our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

\keywords{Authors' choice; of terms; separated; by semi\-colons;
  commas, within terms only; this section is required.}

\category{H.5.m.}{Information Interfaces and Presentation
  (e.g. HCI)}{Miscellaneous} \category{See
  \url{http://acm.org/about/class/1998/} for the full list of ACM
  classifiers. This section is required.}{}{}

\section{Introduction}
There are many tasks that are trivial for people, but difficult to solve
programmatically.  
Typical tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
%judging the relevancy or quality of content,
and performing surveys for 
academic or market research purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
microtask platform).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
Many tasks are ill-defined, in the sense that they do not have
a clear ``correct'' response, and require high-level, qualitative judgment.
Microtask platforms are marketplaces that help fill the gap in current 
computational capabilities, by matching requesters, who need to have such 
tasks completed, with human workers.  Amazon's Mechanical Turk, and 
CrowdFlower are two popular microtask platforms.

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, the typical microtask setup creates the conditions in which
earlier tasks could induce bias in later ones, through priming.

We seek to determine if any significant priming effect occurs between
tasks, and if so, to measure and characterize it.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  To provide a generalized measure of bias, we seek to quantify the
extent to which intertask priming can shift the distribution of responses 
to a task.  
Measuring the \textit{extent} of the shift in response distribution,
i.e. the extent of bias, is substantially harder than
simply determining \textit{whether} a biasing effect has occurred.  
Our first contribution is a statistically grounded method for doing so.

@@

Our results show that a worker's responses are strongly influenced by 
the content of tasks performed beforehand, leading to as much as 50\%
bias (measured as total variational distance, 
see Figure~\ref{fig:l1_example} for illustrative definition).  
Using the WordNet 
knowledge base, we analyze worker's word choices to characterize 
the nature of these effects in detail.  We find that, when workers 
label a series of images that are more similar, their responses become 
more specialized more diverse.  Prior tasks can shift the topical focus of 
worker's labels, inducing them to focus on different aspects of the images.

As a point of comparison, we perform similar experiments, in which we
alter the framing of microtask assignments, in terms of the stated purpose
of the task.  Remarkably, the effects prior microtasks themselves,
which are virtually ubiquitous, are on par with, or stronger than, 
overtly framing the purpose of an assignment.

@@

% These things are definitely not assured, and people have tried to 
% figure out what to do about it
Accuracy and replicability are central to any crowdsourcing study.
There is ongoing research investigating how the design of microtasks,
and their context, affect the quality of responses.  
One of the most basic issues with crowd work
is that workers vary in the amount of attention they pay to tasks, 
and in their understanding of instructions.
Workers who disregard or misunderstand instructions can be effectively 
screened out by including quiz-questions among the tasks, while
instruction comprehension can be improved using a training phase before
actual tasks begin
\cite{le2010ensuring,kazai2013analysis}. %paolacci2010running},
In addition, providing real-time feedback to workers encourages  
higher-quality responses, while prompting workers to review their work
according to a set of criteria increases the worker's response quality 
over time \cite{Dow20121013}.

@@

% Task pricing
Since microtask work is generally paid, wage is a basic parameter in
the requesters control that might influence response quality.
One might expect a higher wage to \textit{buy} better performance,
but results are ambiguous.  One study found that increasing wage
has no effect on response quality, but does increase the amount of 
responses \cite{Mason200977}.
Another study \cite{kazai2013analysis} showed that increasing
wages does increase quality, but that this effect saturates, and 
eventually increases in wage attract a larger proportion of workers who 
disregard the task instructions.

@@

% Optimization based on the breakdown of tasks
Breaking down of complex jobs into simpler tasks, can increasing worker
efficiency by enabling greater parallelism.
While this could disrupt the natural context provided by performing the
whole job as a single task, it turns out that, 
for complex tasks such as writing an article, 
dividing the job into subtasks, including outlining, 
information-gathering, and paragraph-synthesis, actually improves the
quality of the end-product \cite{kittur2011crowdforge}.

@@

\subsection{Priming}
Priming is a psychological phenomenon whereby previous exposure to a 
stimulus leads to faster or more accurate responses to similar stimuli 
\cite{Ghuman17062008},
or to lower response thresholds \cite{BJOP1826}.  
Priming occurs by means of pre-activation, which can influence
stimulus encodings (during perception) \cite{BJOP1826}, 
the top-down application of object-knowledge \cite{Ghuman17062008},
and memory access \cite{beller1971priming}.
Priming is more 
effective when the prime and the target task involve the kind of 
activity.  For example, exposing participants to an image helps them 
subsequently recognize that image when shown very briefly in a 
tachistoscope; however, being presented with a related \textit{word}, 
and reading it aloud, does not \cite{BJOP1796}.

As we have mentioned, workers prefer to perform series of similar tasks
series of similar tasks in quick succession.  Moreover, the many 
microtasks involve tasks based on visual and auditory perception 
similar to the kinds used in priming studies.
Thus, in a typical microtask assignment, there are many opportunities for 
priming, the effects of which should be explored.

\subsection{Measuring the extent of priming}
If a prior task acts as a prime for a later one, it will 
result in a shift in the responses workers provide for the later task.
A variety of tests exist to determine \textit{whether} two samples, 
i.e. sets of responses, come from different distributions, 
most notably the $\chi^2$ test.  
This will suffice to determine whether there are any grounds for concern 
about priming effects in the first place.  However, such tests
do not tell us \textit{how much} two distributions differ, and hence
how severe the priming effects are.

Determining the severity of priming effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions, by
sampling responses from workers exposed to different priming conditions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulation such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be calculated from the total variational
  distance
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=30\%$ and $\theta=50\%$ 
respectively.

\begin{figure}
	\centering
	\includegraphics[scale=1.0]{figs/normal_example.pdf}
	\caption{
	  	Normal distributions exhibiting a total variational distance
		of A) 50\% and B) 30\%.  The total variational distance is 
		the non-overlapping portion of the distributions, e.g. in
		A) it is given by 
		$\theta = a_1 / (a_1 + a_2) = a_2 / (a_2 + a_3)$.
	}
	\label{fig:l1_example}
\end{figure}

@@

However, we can establish a lower bound for $\theta$ by 
exploiting a fact about the theoretical limits on the accuracy of a 
classifier algorithm.  The intuition is as follows: 
suppose workers are shown one of two alternative designs\footnote{We will
use ``design'' in a general sense, to include both the design of the task
and of its context.  In particular, the ``design'' might include the
particular tasks that were shown beforehand, or the use of framing.}
for an otherwise
similar task, and that we build a classifier which, 
based on a worker's response, infers which of the designs had been 
used.
If worker's responses are not affected by the design alternative,
then the classification problem will be hard, and the classifier's 
accuracy poor.
Conversely, if the classifier accuracy is good, then design alternative 
must have a strong effect on the response distribution.

@@

We performed a series of five experiments
on Amazon's Mechanical Turk\footnote{\url{mturk.com}} using 1071 workers.  
Every experiment consisted of two treatments, each with 119 workers,
who performed a single assignment\footnote{Workers could not participate 
multiple times in our study}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
assignments are called Human Intelligence Tasks (HITs), but this use of 
``task'' is 
different from our current one: in our experiment each HIT actually 
involves 10 image-labeling tasks.}.  
The setup in each experiment followed the template depicted in 
Figure~\ref{fig:task-schematic}.  
The assignments had two parts.  The first part of the assignment differed
between the two treatments, and consisted of a set of initial tasks 
and/or framing (by describing the purpose of the assignment or source of 
funding).  In the second part of the assignment, workers from both
treatments completed the same five \textit{test tasks}.  Each of the 
initial and test tasks required workers to provide five descriptive labels
for an image.  The tasks were performed one at a time,
and, in treatments involving both initial and test tasks, there was no
interruption or distinction made between the initial and test tasks from
the perspective of the worker.

@@

The frequencies of words used by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks (by $\chi^2$ test, $p = 6.0 \times 10^{-14}$),
even though the test tasks were identical in both treatments.  
Thus earlier tasks do significantly affect later ones, which 
validates our concerns about the typical microtask methodology.

Having affirmed the \textit{existence} of intertask effects, we sought to
measure the severity of the bias induced, i.e. $\theta$.
To measure $\theta$ we used a na\"ive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the na\"ive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons, is probably a relatively mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We also used a 
support vector machine and found very similar results.

@@

Based on the classifier accuracy, intertask effects in the 
experiment \textit{intertask-food-objects}
lead to (a lower bound) bias of $\theta=30\%$ between workers from the 
\textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
It is difficult to visualize the distributions of word frequencies,
but for reference, the distributions shown in 
Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
substantial potential to distort microtask data.

@@

Framing induced changes in the frequencies of 
word usage at significance 
(as determined by $\chi^2$ test; $p=0.0012$).  But, 
the \textit{extent} of framing-induced bias was not statistically 
distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
And so, remarkably, the extent of bias due to framing was weaker than that 
due to intertask effects ($p=2.1\times 10^{-5}$).
In other words, the \textit{microtasks themselves}
had a stronger biasing effect than framing.

To assess the persistence of intertask effects, we replicated the 
\textit{intertask-food-objects} experiments, rotating the ordering of the
test tasks, so that each test task occupied each of the possible 5 
test-task positions (see Figure \ref{fig:task-schematic}).  
By taking the average bias induced for each test task when 
occupying a given position, we determined $\theta$ as a function of the 
task position.
Bias was strongest for the first test task (about 28\%), 
but remained significant through all five test tasks 
($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
tasks were separated by four intervening tasks (Figure~\ref{fig:theta}B).

@@

Results for this experiment again showed a 
strong bias as a result of intertask effects (about 50\%) 
(Figure~\ref{fig:theta}A).  Again, visualizing the word frequencies 
themselves is difficult, but Figure~\ref{fig:l1_example} provides an 
example of distributions having $\theta = 50\%$.

@@

It was only when framing was combined with an active reiteration step, 
that framing-induced bias reached a comparable extent to that induced by 
intertask effects.  In the experiment \textit{echo-food-objects},
after framing the purpose of the task (as the recognition of food
or objects), workers were asked to echo the purpose of the task
using a combo-box input.  This  ``echoed framing'' induced a bias of about 
35\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
should be considered as a framing treatment \textit{per se}:
requiring the worker to reiterate the purpose signals our intent, as the 
requester, to ensure that the worker has taken note of it, possibly leading 
the worker to interpret the exchange as an instruction.  
In any case, it is remarkable that intertask effects
were on par with an explicit, actively reinforced statement of the tasks' 
purpose.

@@

WordNet provides
hyponym and hypernym relations between words.  A hypernym is a 
generalization (for example, ``bread'' is a hypernym of ``pumpernickel''), 
while a hyponym is a specialization.  We took took the set of food-words
to be all those reachable through
a chain of hyponym relations from the word senses 
\texttt{food.n.01} and \texttt{food.n.02}, in other words, all words
denoting a specific kind of food (a total of 3590 words).  
To improve the coverage of words for
less widespread foods, we augmented this set with all words
discovered while crawling the World Food section of \url{allrecipes.com} 
which were not already in WordNet.

To validate the resulting set of 
food words, three independent annotators labeled 500 words selected from 
workers' responses as either food or non-food, and these were
compared to the labels derived using the automated approach.
Among those words, 26\% were 
deemed to be food by the majority of annotators.  
Taking the majority label among annotators to be the correct one, 
the automatically-identified food-words
had 88\% correspondence to the human annotators.  Treating the
automated identification of food words as another annotator, there 
was an inter-rater reliability of 82.4\%.

Using the automated labeling of food words, we found that, in fact
workers exposed to food (via prior tasks or framing) did not necessarily
use more food-words when labeling images in the test tasks.
In \textit{intertask-food-culture}, food-exposed
workers actually used significantly \textit{fewer} food-related words 
during test tasks (Figure~\ref{fig:specificity}A).  This finding
rules out a seemingly-simple idea that workers emphasize
content that has been present in earlier tasks: seeing content 
influences, but does not necessarily \textit{increase}, the probability of 
referring to it in subsequent tasks.

@@

The observations regarding lexical richness suggest that 
initial tasks might influence workers to use more refined or specialized 
words, when referring to aspects of content that had been present in the 
initial tasks.  
To test this, we used the hypernym and hyponym relations in WordNet 
to operationalize the notion of word specialization.  
Within each experiment, we determined relative specificity
of the food-words, between the treatments using the following equation:
\begin{equation}
	S(P,Q) = \frac{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} - \mathbf{1}_{[v>w]} \right)
	}{
		\sum_{w\in P}\sum_{v\in Q} \left(
			\mathbf{1}_{[w>v]} + \mathbf{1}_{[v>w]} \right)
	},
\end{equation}
where $P$ and $Q$ are sets of words associated to different experimental 
treatments, and $\mathbf{1}_{[w>v]}$ evaluates
to 1 if synset $w$ is more specific than (i.e. is a hyponym of) synset $v$.
The relative specificity lies within $[-1,1]$; 
we report it as a percentage.
In computing this quantity between two treatments, we first computed the 
relative specificity for the treatments separately for each test task, and 
averaged the results obtained across the five test tasks.

>>>>

\begin{abstract}
Microtask platforms are becoming commonplace tools for performing human
research, producing gold-standard data, and annotating large datasets.
These platforms connect \textit{requesters}
(researchers or companies) with large populations (crowds) of workers, who 
perform small tasks, typically taking less than five minutes each.
A topic of ongoing research concerns the design of tasks that elicit high
quality annotations.
Here we identify a feature of nearly all crowdsourcing 
workflows that profoundly impacts workers' responses.
Microtask assignments typically consist of a sequence 
of tasks sharing a common format (e.g., circle galaxies in an image). 
Using image-labeling, a canonical microtask format, we 
discover that earlier tasks have a priming effect on the worker, shifting 
the distribution of future responses by 30-50\% 
(total variational distance). 
Specifically, prior tasks influence the content that workers focus on, 
as well as the richness and specialization of responses. 
We call this phenomenon \textit{intertask effects}.
We compare intertask effects to the overt framing, 
effected by stating the requester's research interest, 
and find that intertask effects are on par or stronger.
While intertask effects can be a source of systematic bias, 
our results suggest that, with appropriate task design, 
they might be leveraged to hone worker focus and acuity, 
helping to elicit reproducible, expert-level judgments.
Intertask effects are a crucial aspect of human computation that should be
considered in the design of any crowdsourced study.
\end{abstract}

\keywords{Microtask; crowdsourcing; priming; task-design; bias; classifier}

\category{H.1.2.}{Information Systems}{Models and Principles}
\category{Human information processing}{}{}

\section{Introduction}
There are many tasks that are trivial for people, but difficult to solve
programmatically.  
Typical tasks include tagging and categorizing images,
%\cite{6116320,Zhai2012357}, 
coding and transcribing media,
%\cite{chandler2013breaking,Berinsky2012351,Finnerty2013},%paolacci2010running},
%judging the relevancy or quality of content,
and performing surveys for 
academic or market research purposes (see Table~\ref{table:task_composition} for a listing of task types seen on the Amazon's Mechanical Turk 
microtask platform).
%\cite{le2010ensuring,grady2010crowdsourcing,alonso2009can,kazai2013analysis}.
Many tasks are ill-defined, in the sense that they do not have
a clear ``correct'' response, and require high-level, qualitative judgment.
Microtask platforms are marketplaces that help fill the gap in current 
computational capabilities, by matching requesters, who need to have such 
tasks completed, with human workers.  Amazon's Mechanical Turk\footnote{\url{mturk.com}}, and 
CrowdFlower\footnote{\url{crowdflower.com}} are two popular microtask 
platforms.

@@

Psychological experiments show that the exposure to stimuli immediately 
before performing a task influences performance, an effect known as 
\textit{priming} \cite{BJOP1796}.
The effect of priming appears to be stronger when the modality of the
prime is the same as the task.
Thus, the typical microtask setup creates conditions in which
earlier tasks could induce bias in later ones, through priming.

We seek to determine if any significant priming effect occurs between
tasks, and if so, to measure and characterize it.
Certain tasks admit a well-defined notion of ``correct'' and 
``incorrect'' responses.  But many tasks involving qualitative judgment
do not.  Rather than simply characterizing effects on accuracy, we seek
to provide a generalized measure of bias, by quantifying the
extent to which intertask effects can shift the distribution of responses 
to a task.  
Measuring the \textit{extent} of the shift in response distribution,
i.e. the extent of bias, is substantially harder than
simply determining \textit{whether} a biasing effect has occurred.  
Our first contribution is a statistically grounded method for doing so.

@@

Our results show that a worker's responses are strongly influenced by 
the content of tasks performed beforehand, leading to as much as 50\%
bias (measured as total variational distance, 
see Figure~\ref{fig:l1_example} for illustrative definition).  
Using the WordNet 
knowledge base, we analyze worker's word choices to characterize 
the nature of these effects in detail.  We find that, when workers 
label a series of images that are more similar, their responses become 
more specialized and more diverse.  
Prior tasks can shift the topical focus of 
worker's labels, inducing them to focus on different aspects of the images.

As a point of comparison, we perform similar experiments, in which we
alter the framing of microtask assignments, in terms of the stated purpose
of the task, or by naming the funder.
Remarkably, the effects of prior microtasks themselves,
which are virtually ubiquitous, are on par with, or stronger than, 
overtly framing an assignment.

@@

% These things are definitely not assured, and people have tried to 
% figure out what to do about it
There is ongoing research investigating how the design of microtasks,
and their context, affect the quality of responses.  
One of the most basic issues with crowd work
is that workers vary in the amount of attention they pay to tasks, 
and in their understanding of instructions.
Workers who disregard or misunderstand instructions can be effectively 
screened out by including quiz-questions among the tasks, while
instruction comprehension can be improved using a training phase before
actual tasks begin
\cite{le2010ensuring,kazai2013analysis}. %paolacci2010running},
In addition, providing real-time feedback to workers encourages  
higher-quality responses, while prompting workers to review their work
according to a set of criteria increases the worker's response quality 
over time \cite{Dow20121013}.

@@

% Task pricing
Since microtask work is generally paid, wage is a basic parameter in
the requester's control that might influence response quality.
One might expect a higher wage to \textit{buy} better performance,
but results are ambiguous.  One study found that increasing wage
has no effect on response quality, but does increase the amount of 
responses \cite{Mason200977}.
Another study \cite{kazai2013analysis} showed that increasing
wages does increase quality, but that this effect saturates, and 
eventually increases in wage attract a larger proportion of workers who 
disregard the task instructions.

@@

% Optimization based on the breakdown of tasks
The breaking down of complex jobs into simpler tasks can increase
efficiency by enabling greater parallelism.
While this could disrupt the natural context provided by performing the
whole job as a single task, it turns out that, 
for complex tasks such as writing an article, 
dividing the job into subtasks, including outlining, 
information-gathering, and paragraph-synthesis, actually improves the
quality of the end-product \cite{kittur2011crowdforge}.

@@

\subsection{Priming}
Priming is a psychological phenomenon whereby previous exposure to a 
stimulus leads to faster or more accurate responses to similar stimuli 
\cite{Ghuman17062008},
or to lower response thresholds \cite{BJOP1826}.  
Priming occurs by means of pre-activation, which can influence
stimulus encodings (during perception) \cite{BJOP1826}, 
the top-down application of object-knowledge \cite{Ghuman17062008},
and memory access \cite{beller1971priming}.
Priming is more 
effective when the prime and the target task involve the same kind of 
activity.  For example, exposing participants to an image helps them 
subsequently recognize that image when shown very briefly in a 
tachistoscope; however, being presented with a related \textit{word}, 
and reading it aloud, does not \cite{BJOP1796}.

As we have mentioned, workers prefer to perform a series of tasks that
are similar to one another.
Moreover, many 
microtasks involve tasks based on visual and auditory perception 
similar to the kinds used in priming studies.
Thus, in a typical microtask assignment, there are many opportunities for 
priming, the effects of which should be explored.

\section{Measuring the extent of priming}
If a prior task acts as a prime for a later one, 
and thereby introduces bias, the bias will manifest as
a shift in the distribution of responses 
workers provide for the later task.
A variety of tests exist to determine \textit{whether} two samples, 
i.e. sets of responses, come from different distributions, 
most notably the $\chi^2$ test.  
This will suffice to determine whether there are any grounds for concern 
about priming effects in the first place.  However, such tests
do not tell us \textit{how much} two distributions differ, and hence
how severe the priming effects are.

Determining the severity of priming effects amounts to measuring a 
distance, or \textit{divergence}, between response distributions, by
sampling responses from workers exposed to different priming conditions.
We will present a method for bounding a kind of divergence known as 
\textit{total variational distance}\footnote{
  Other formulations such as the Kullback-Leibler and 
  Jensen-Shannon divergence can be calculated from the total variational
  distance.
}, which we will henceforth denote by $\theta$.
The value of $\theta$ between two distributions $P$ and $Q$ 
is the fraction under the graph of $P$ that does not overlap with that
under $Q$ (or vice-versa; see Figure~\ref{fig:l1_example}).  
Formally:
\begin{align}
	\theta = \frac{1}{2}\sum_{x \in X} \left| p(x) - q(x) \right|,
	\label{eq:theta}
\end{align}
Where $p(x)$ and $q(x)$ are the respective probabilities 
that a worker submits response $x$, from a set of possible responses 
$\mathcal{X}$, under distributions $P$ and $Q$.
The divergence is constrained to 
$0 \leq \theta \leq 1$ (or from 0 to 100\%).
When $\theta = 100\%$, the distributions do not overlap at all.  
When $\theta = 0\%$, the distributions are identical.
For reference, the distributions plotted in 
Figure~\ref{fig:l1_example}A and B have $\theta=50\%$ and $\theta=30\%$ 
respectively.

\begin{figure}
	\centering
	\includegraphics[scale=1.0]{figs/normal_example.pdf}
	\caption{
	  	Normal distributions exhibiting a total variational distance
		of A) 50\% and B) 30\%.  The total variational distance is 
		the non-overlapping portion of the distributions, e.g. in
		A) it is given by 
		$\theta = a_1 / (a_1 + a_2) = a_3 / (a_2 + a_3)$.
	}
	\label{fig:l1_example}
\end{figure}

@@

Nevertheless, we can establish a lower bound for $\theta$ by 
exploiting a fact about the theoretical limits on the accuracy of a 
classifier algorithm.  The intuition is as follows: 
suppose workers are shown one of two alternative designs\footnote{We
use ``design'' in a general sense, to include both the design of the task
and of its context.  In particular, the ``design'' might include the
selection of tasks that were shown beforehand, or the use of framing.}
for an otherwise
similar task, and that we build a classifier which, 
based on a worker's response, infers which of the designs had been 
used.
If worker's responses are not affected by the design alternative,
then the classification problem will be hard, and the classifier's 
accuracy poor.
Conversely, if the classifier accuracy is good, then design alternative 
must have had a strong effect on the response distribution.

@@

We performed a series of five experiments
on Amazon's Mechanical Turk using 1071 workers.  
Every experiment consisted of two treatments, each with 119 workers,
who performed a single assignment\footnote{Workers could not participate 
multiple times in our study.}\textsuperscript{,}\footnote{On Mechanical Turk, individual 
assignments are called Human Intelligence Tasks (HITs), but this use of 
``task'' is 
different from our current one: in our experiment each HIT actually 
involves 10 image-labeling tasks.}.  
The setup in each experiment followed the template depicted in 
Figure~\ref{fig:task-schematic}.  
The assignments had two parts.  The first part of the assignment differed
between the two treatments, and consisted of a set of initial tasks 
and/or framing (by describing the purpose of the assignment or source of 
funding).  In the second part of the assignment, workers from both
treatments completed the same five \textit{test tasks}.  Each of the 
initial and test tasks required workers to provide five descriptive labels
for an image.  The tasks were performed one at a time,
and, in treatments involving both initial and test tasks, there was no
interruption or distinction made between the initial and test tasks from
the perspective of the worker.

@@

The frequencies of words used by
workers in the \textit{food} and \textit{objects} treatments differed
significantly during test tasks ($p = 6.0 \times 10^{-14}$),
even though the test tasks were identical in both treatments.  
Thus earlier tasks do significantly affect later ones, which 
validates our concerns about the typical microtask methodology.

The heterogeneity of word-frequencies between treatments was based on 
Pearson's $\chi^2$ test with Yates' correction.
In linguistics applications, the use of a $\chi^2$ to test for 
heterogeneity between corpora has been called
into question, because there is frequently heterogeneity \textit{within}
a given corpus \cite{kilgarriff1996comparing}.
This occurs because certain documents in a corpus will regard certain 
topics, leading to bursty word usage.  While our setup is substantially
remote from the applications for which this concern was raised, 
one could argue that the responses to a given treatment
constitute a ``corpus'', and the responses of a given worker to a 
``document''.
To address this concern, we randomly split responses to given treatment
into two sets, and tested for hetererogeneity between the sets.
In all cases, we failed to find heterogeneity \textit{within} a given 
treatment (with $p > 0.3$ for all treatments and $p > 0.8$ for most).
Thus, the heterogeneity we observed \textit{between} treatments is 
meaningful.

Having affirmed the \textit{existence} of intertask effects, we sought to
measure the severity of the bias induced, i.e. $\theta$.
To measure $\theta$ we used a na\"ive Bayes classifier based on a 
multinomial distribution over the word frequencies in worker's labels, 
and measured it's accuracy using leave-one-out cross-validation.  
We chose the na\"ive Bayes
classifier for three reasons.  First, it performs well even when the 
number of features is large compared to the number of training examples
\cite{bickel2004,hastie2009elements}.  
Second, there are no hyperparameters to 
optimize, which eliminates the need to partition the response data into
dev and test sets.
Third, the conditional independence assumption, normally 
undertaken for pragmatic reasons \cite{Zhang2004562}, 
is probably a relatively mild in 
relation to image labels, since they are likely to be less dependent
on one another than in a coherent passage of text.  We repeated our
analysis used a support vector machine and found very similar results.

@@

Based on the classifier accuracy, intertask effects in the 
experiment \textit{intertask-food-objects}
lead to (a lower bound) bias of $\theta=30.6\%$ between workers from the 
\textit{food} and \textit{objects} treatments (Figure~\ref{fig:theta}A).
It is difficult to visualize the distributions of word frequencies,
but for reference, the distributions shown in 
Figure~\ref{fig:l1_example}B have $\theta = 30\%$.  This represents a 
substantial potential to distort microtask data.

When observing the classifier's accuracy, in order to calculate $\theta$,
the number of correct inferences made by the classifier follows a binomial 
distribution.  The fraction of successes yields the maximum likelihood
estimate of the classifier's accuracy (used to generate $\theta$), 
and we derived confidence intervals using the exact Clopper-Pearson method.

@@

Framing induced changes in the frequencies of 
word usage at significance 
(as determined by $\chi^2$ test; $p=0.0012$).  But, 
the \textit{extent} of framing-induced bias was not statistically 
distinguishable from zero ($p =0.37$) (Figure~\ref{fig:theta}A).
And so, remarkably, the extent of bias due to framing was weaker than that 
due to intertask effects ($p=2.1\times 10^{-5}$)\footnote{To compare bias
  due to framing and inter-task effects, we approximated the distribution
  of correct classifications as a normal distribution, and performed
a (two-tailed) two-proportion $z$-test.}.
In other words, the \textit{microtasks themselves}
had a stronger biasing effect than framing.

To assess the persistence of intertask effects, we replicated the 
\textit{intertask-food-objects} experiments, rotating the ordering of the
test tasks, so that each test task occupied each of the possible 5 
test-task positions (see Figure \ref{fig:task-schematic}).  
By taking the average bias induced for each test task when 
occupying a given position, we determined $\theta$ as a function of the 
task position.
Bias was strongest for the first test task (28.1\%), 
but remained significant through all five test tasks 
($\alpha=0.05$) sustaining over 12\% bias even when the initial and test 
tasks were separated by four intervening tasks (Figure~\ref{fig:theta}B).

@@

Results for this experiment again showed a 
strong bias as a result of intertask effects (51.3\%) 
(Figure~\ref{fig:theta}A).  Again, visualizing the word frequencies 
themselves is difficult, but Figure~\ref{fig:l1_example} provides an 
example of distributions having $\theta = 50\%$.

@@

It was only when framing was combined with an active reiteration step, 
that framing-induced bias reached a comparable extent to that induced by 
intertask effects.  In the experiment \textit{echo-food-objects},
after framing the purpose of the task (as the recognition of food
or objects), workers were asked to echo the purpose of the task
using a combo-box input.  This  ``echoed framing'' induced a bias of 
36.1\% (Figure~\ref{fig:theta}A). However, it is difficult to say whether this 
should be considered as a framing treatment \textit{per se}:
requiring the worker to reiterate the purpose signals our intent, as the 
requester, to ensure that the worker has taken note of it, possibly leading 
the worker to interpret the exchange as an instruction.  
In any case, it is remarkable that intertask effects
were on par with an explicit, actively reinforced statement of the tasks' 
purpose.

@@

WordNet provides
hyponym and hypernym relations between words.  A hypernym is a 
generalization (for example, ``bread'' is a hypernym of ``pumpernickel''), 
while a hyponym is a specialization.  We took took the set of food-words
to be all those reachable through
a chain of hyponym relations from the word-senses 
\texttt{food.n.01} and \texttt{food.n.02}, in other words, all words
denoting a specific kind of food (a total of 3590 words).  
To improve the coverage of words for
less widespread foods, we augmented this set with all words
discovered while crawling the World Food section of \url{allrecipes.com} 
which were not already in WordNet.

To validate the resulting set of 
food words, three independent annotators labeled 500 words selected from 
workers' responses as either food or non-food, and these were
compared to the labels derived using the automated approach.
Among those words, 26\% were 
deemed to be food by the majority of annotators.  
Taking the majority label among annotators to be the correct one, 
the automatically-identified food-words
had 88\% correspondence to the human annotators.  Treating the
automated identification of food words as another annotator, there 
was an 82.4\% agreement between annotators.

Using the automated labeling of food words, we found that, contrary to
expectations,
workers exposed to food (via prior tasks or framing) did not necessarily
use more food-words when labeling images in the test tasks.
In \textit{intertask-food-culture}, food-exposed
workers actually used significantly\footnote{
  Frequencies of food references within a treatment were calculated as
  an average across workers, and modeled as normally distributed.
} \textit{fewer} food-related words 
during test tasks (Figure~\ref{fig:specificity}A).  This finding
rules out a seemingly-simple idea that workers emphasize
content that has been present in earlier tasks: seeing content 
significantly influences, but does not necessarily 
\textit{increase}, the probability of referring to it in subsequent tasks.

@@

To test the significance of the difference in sizes of food
lexicons,
we created a null model for each experiment, by assuming that
responses for both treatments were in fact drawn from the same 
distribution.
This was accomplished by pooling responses for both treatments 
of a given experiment, then 
drawing two bootstrap samples of 119 responses and calculating
the difference in the size of their food lexicons.  
We repeated this 1000 times and took the 2.5th and 97.5th percentiles 
as the critical values for the rejection of the null hypothesis 
(the latter shown by stars in Figure~\ref{fig:specificity}B).
